---
title: "CalculatingPES"
author: "Miriam Yang"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(bruceR)
library(psych)
library(ggplot2)

```

# Importing datasets
```{r}

Flanker <- read_csv("/Users/miriam/Documents/PES_Project/ReadytoAnalyseData/Flanker.csv")
Numerical <- read_csv("/Users/miriam/Documents/PES_Project/ReadytoAnalyseData/Numerical.csv")
Science <- read_csv("/Users/miriam/Documents/PES_Project/ReadytoAnalyseData/G2Science.csv")

```



# Define the function to calculate PES and PEA
```{r Writing the function}

##### equation:
# - PES traditional = MRTpostEC -  MRTpostCC
# - PES robust = MRTcceCc - MRTcCecc
# - PES error = MRTcceCc - MRTccEc

##### Condition 1: Determine if accuracy == 0
##### Condition 2: Determine if accuracy == 1
##### Condition 3: Determine ccEcc
## PES calculation

PEScalculator <- function(df){
 df[,"condition1"] <- df[,"Accuracy"] == 0 
 df[,"condition2"] <- df[,"Accuracy"] == 1
 
 for(i in which(df[,"Accuracy"] == 0)){
    if(nrow(df)>i && 
       df[i+1,"Accuracy"] == 1 &&  
       df[i-1,"Accuracy"] == 1 && 
       df[i+2,"Accuracy"] == 1 &&
       df[i-2,"Accuracy"] == 1 )           
    df[i,"ccEcc"] <- df[i,"RT"] 
    
    if(nrow(df)>i &&
       df[i+1,"Accuracy"] == 1)                              
    df[i+1,"postE"] <- df[i+1,"RT"]  # postE: Post-error correct 
 } 

  df[,"condition3"] <- !is.na(df[,"ccEcc"])

 for (k in which(df[, "condition3"] == TRUE)) {
   if(nrow(df)>k)
     df[k+1,"cceCc"] <- df[k+1,"RT"] # cceCc: post error pre correct 
     df[k-1,"cCecc"] <- df[k-1,"RT"] # cCecc: post correct pre error
 
 }
 
for(j in which(df[, "Accuracy"] == 1)){
  if(nrow(df)>j &&
       df[j+1,"Accuracy"] == 1)
    df[j+1,"postC"] <- df[j+1,"RT"] # postC: post correct correct items
 }
 return(df)
}

# # G2 & G4 Science data need to be run separately as function throws error.
# 
# df <- G4Science
# 
# df[,"condition1"] <- df[,"Accuracy"] == 0
# df[,"condition2"] <- df[,"Accuracy"] == 1
# 
#  for(i in which(df[,"Accuracy"] == 0)){
#     if(nrow(df)>i &&
#        df[i+1,"Accuracy"] == 1 &&
#        df[i-1,"Accuracy"] == 1 &&
#        df[i+2,"Accuracy"] == 1 &&
#        df[i-2,"Accuracy"] == 1 )
#     df[i,"ccEcc"] <- df[i,"RT"]
# 
#     if(nrow(df)>i &&
#        df[i+1,"Accuracy"] == 1)
#     df[i+1,"postE"] <- df[i+1,"RT"]  # postE: Post-error correct
#  }
# 
#   df[,"condition3"] <- !is.na(df[,"ccEcc"])
# 
#  for (k in which(df[, "condition3"] == TRUE)) {
#    if(nrow(df)>k)
#      df[k+1,"cceCc"] <- df[k+1,"RT"] # cceCc: post error pre correct
#      df[k-1,"cCecc"] <- df[k-1,"RT"] # cCecc: post correct pre error
# 
#  }
# 
# for(j in which(df[, "Accuracy"] == 1)){
#   if(nrow(df)>j &&
#        df[j+1,"Accuracy"] == 1)
#     df[j+1,"postC"] <- df[j+1,"RT"] # postC: post correct correct items
# }
# 
# G4Science1 <- df
# 

## Calculate post error accuracy
## PEA(post-error accuracy), PCA(post-correct accuracy)
## PEE(post-error error), PCE(post-correct eorror)
PEAcalculator <- function(df){
 for(i in which(df[,"Accuracy"] == 0)){
   df[i, "Error"] <- "Yes"
  if(nrow(df)>i &&
     df[i+1,"Accuracy"] == 1)           
    df[i+1,"PEC"] <- "Yes"
  if(nrow(df)>i &&
     df[i+1,"Accuracy"] == 0) 
    df[i+1,"PEE"] <- "Yes" 
 }
 for(i in which(df[,"Accuracy"] == 1)){
  if(nrow(df)>i &&
     df[i+1,"Accuracy"] == 1)           
    df[i+1,"PCC"] <- "Yes"
  if(nrow(df)>i &&
     df[i+1,"Accuracy"] == 0) 
    df[i+1,"PCE"] <- "Yes"
}
return(df)
}

```


# PES and PEA calculation
```{r Running the functions to calculate PES and PEA}

## This process would take around 30-40min..

Flanker1 <- Flanker %>%
  group_by(RandomID) %>%
  PEScalculator() 

Numerical1 <- Numerical %>%
  group_by(RandomID) %>%
  PEScalculator() 

Science1 <- Science %>%
  group_by(RandomID) %>%
  PEScalculator() 

####################################

Flanker1 <- Flanker1 %>%
  group_by(RandomID) %>%
  PEAcalculator() 

Numerical1 <- Numerical1 %>%
  group_by(RandomID) %>%
  PEAcalculator() 

Science1 <- Science1 %>%
  group_by(RandomID) %>%
  PEAcalculator() 

Alltrial <- rbind(Flanker1, Numerical1, Science1)

test <- Flanker1 %>%
  group_by(RandomID, Group) %>%
  mutate(abc = mean(postC, na.rm = T))
    mutate(PESmean = colMeans(matrix(Numerical1$cceCc, nrow=30), na.rm = T))

NumcceCc <- colMeans(matrix(Numerical1$cceCc, nrow=30), na.rm = T)


### Change parameters in the following for loop
pid <- -1
block <- c()
block_count = 0
for (i in Science1$RandomID) {
  if (i != pid) {
    pid = i
    block <- c(block, 0)
    block_count = 0
  } else {
    block_count <- block_count + 1
    block <- c(block, floor(block_count/30))
  }
}


Flanker1$block <- block + 1 
Numerical1$block <- block  + 1
Science1$block <- block  + 1

write_csv(Flanker1, "ReadytoAnalyseData/Flanker.csv")
write_csv(Numerical1, "ReadytoAnalyseData/Numerical.csv")
write_csv(Science1, "ReadytoAnalyseData/Science.csv")


```


The following ID return non 360 rows:
ID 12832 only show 40 trials in the science task (Removed)
ID 23072, Duplicate ID, same ppt, removed the second attempt
ID 37431, Duplicate ID, two ppts, change the one in Group 3 to 37432, done
ID 47925 Duplicate ID, two ppts, change the one in Group 3 to 47926, done
ID 86691 Duplicate ID, two ppts, change the one in Group 4 to 86691, done

```{r Average}

# Check if every participant got 360 rows of trial, and check if there are multiple record for one participant.

Alldata3 %>%
   dplyr::group_by(RandomID) %>%
   dplyr::summarize(sum = sum(length(RandomID))) %>%
  filter(sum != 360)

```

```{r Duplicate ID 32757}

Alltrial$RandomID <- ifelse(Alltrial$Localtime == "2021-08-05_19h52.33.283",
               "32758", Alltrial$RandomID)

filter(test, RandomID == "32758")
Alltrial <- mutate(Alltrial, RandomID == ifelse(RandomID == "32757" &
                                            Localtime == "2021-08-05_19h52.33.283",
                                           32758, RandomID))
write_csv(Alltrial, "ReadytoAnalyseData/Alltrial_566.csv")

```

 
```{r Calculating Individuals' metrics}
# detach(package:Rmisc)
## PEA = PEC/PEE+PEC
## PCA = PCC/PCE+PCC

Average <- Alltrial %>%
  mutate(RTcorr = case_when(Accuracy == 1 ~ RT),
           RTincorr = case_when(Accuracy == 0 ~ RT)) %>%
  group_by(RandomID, Group, Task, Localtime) %>%
  dplyr::summarize(RT = mean(RT, na.rm = T),
            RTcorr = mean(RTcorr, na.rm = T),
            RTincorr = mean(RTincorr, na.rm = T),
            cceCc = mean(cceCc, na.rm = T),
            cCecc = mean(cCecc, na.rm = T),
            postE = mean(postE, na.rm = T),
            postC = mean(postC, na.rm = T),
            PEC = sum(PEC == "Yes", na.rm = T),
            PEE = sum(PEE == "Yes", na.rm = T),
            PCC = sum(PCC == "Yes", na.rm = T),
            PCE = sum(PCE == "Yes", na.rm = T),
            Corr = sum(Accuracy == 1, na.rm = T),
            Incorr = sum(Accuracy == 0, na.rm = T)) %>%
  mutate(PEStrad = postE - postC,
         PESrobust = cceCc - cCecc,
         PEA = PEC/(PEC + PEE),
         PCA = PCC/(PCC + PCE),
         CorrRate = Corr/120,
         IncorrRate = Incorr/120) %>%
  mutate(Feedback = case_when(Group == "Group1_PES_Task" ~ "Feedback",
                              Group == "Group2_PES_Task" ~ "Feedback",
                              Group == "Group3_PES_Task" ~ "Control",
                              Group == "Group4_PES_Task" ~ "Control"))
# grepl("CA", x)
```

