---
title: "Untitled"
author: "Yiqiong Yang (Miriam)"
date: "2022-08-30"
output: html_document
---

This markdown documents the cleaning process of the data from the PES calculation markdown. 
path = ("ReadytoAnalyseData/PESPEA_Calculating.Rmd")

This process include calculating the average PES, PEA, correct and incorrect rate for each participant.

The cleaning process and decision making 

ID 57502 & 94470 incorr rate too high in Flanker
ID 57502 Incorr 118, 
ID 94470 Incorr 116
Decision: The two participants' data got removed because it seems that they did not understand the task rule and made too many mistakes 

Regarding the outlier treatment, we have trimmed 28 PEStrad and 31 PESrobust by the mean+-sd.

After the outlier treatment, we replaced all NA in flanker with 0. 

```{r Set up and loading data}

require(tidyverse)
require(jtools)
library(dplyr)

Alltrial <- read_csv("ReadytoAnalyseData/Alltrial_566.csv")

```

```{r Calculate average}
# detach(package:Rmisc)

Average <- Alltrial %>%
  mutate(RTcorr = case_when(Accuracy == 1 ~ RT),
           RTincorr = case_when(Accuracy == 0 ~ RT)) %>%
  group_by(RandomID, Group, Task) %>%
  dplyr::summarize(RT = mean(RT, na.rm = T),
            RTcorr = mean(RTcorr, na.rm = T),
            RTincorr = mean(RTincorr, na.rm = T),
            cceCc = mean(cceCc, na.rm = T),
            cCecc = mean(cCecc, na.rm = T),
            postE = mean(postE, na.rm = T),
            postC = mean(postC, na.rm = T),
            PEC = sum(PEC == "Yes", na.rm = T),
            PEE = sum(PEE == "Yes", na.rm = T),
            PCC = sum(PCC == "Yes", na.rm = T),
            PCE = sum(PCE == "Yes", na.rm = T),
            Corr = sum(Accuracy == 1, na.rm = T),
            Incorr = sum(Accuracy == 0, na.rm = T)) %>%
  mutate(PEStrad = postE - postC,
         PESrobust = cceCc - cCecc,
         PEA = PEC/(PEC + PEE),
         PCA = PCC/(PCC + PCE),
         CorrRate = Corr/120,
         IncorrRate = Incorr/120) %>%
  mutate(Feedback = case_when(Group == "Group1_PES_Task" ~ "Yes",
                              Group == "Group2_PES_Task" ~ "Yes",
                              Group == "Group3_PES_Task" ~ "No",
                              Group == "Group4_PES_Task" ~ "No"))

write_csv(Average, "ReadytoAnalyseData/Average_561_NAreplaced.csv")


```

```{r Checking and removing outliers}

Average <- read_csv("ReadytoAnalyseData/Average_561_NAreplaced.csv")


## Checking outliers

upper <- function(x) {
  a = mean(x, na.rm = T)
  b = sd(x, na.rm = T)
  uppervalue = a+3*b
  ifelse(x > uppervalue, uppervalue, x)
}

lower <- function(x) {
  a = mean(x, na.rm = T)
  b = sd(x, na.rm = T)
  lowervalue = a-3*b
  ifelse(x < lowervalue, lowervalue, x)
}

# Code below doesnt seem to work?

windsorise <- function(x){
  a = mean(x, na.rm = T)
  b = sd(x, na.rm = T)
  uppervalue = a+3*b
  lowervalue = a-3*b
  ifelse(lower(x), lowervalue, x) 
  ifelse(upper(x), uppervalue, x)
}

# Determine values fall out of normal range, replace them with 100, as to differentiate from NA from participant make 0 mistakes.


Average <- Average %>%
  group_by(Task) %>%
  mutate_at(vars(PEStrad, PESrobust),
            upper) %>%
  mutate_at(vars(PEStrad, PESrobust),
            lower) 

write_csv(Average, "ReadytoAnalyseData/Average_OutlierRm.csv")

```


```{r}
# png("RTtypedistribution.png", width = 600, height = 600)
# Average %>% 
#   gather("Type", "RT", 9:12) %>%
#   ggplot(aes(RT, colour = Type)) +
#   geom_histogram(binwidth = 0.3, alpha = 0.3) +
#   facet_wrap(vars(Task)) +
#   labs(y = "RT", x = "Task",
#         title = "Distribution of RT type by Task") +
#   theme_apa() +
#   theme(legend.position = "bottom") 
# dev.off
# 
# png("PEStypedistribution.png", width = 1000, height = 800)
# df %>%
#   dplyr::rename(PEStrad_no_outlier = 26) %>%
#   dplyr::rename(PESrobust_no_outlier = 27) %>%
#   gather("Type", "PES", 19,20,26,27) %>%
# ggplot(aes(PES, colour = Task)) +
#   geom_histogram(binwidth = 0.3, alpha = 0.8) +
#   facet_grid(Type ~ Task) +
#     labs(y = "Post-error Slowing", x = "Task",
#         title = "Distribution of PES type by Task") +
#   theme_apa() +
#   theme(legend.position = "none")
# dev.off
# Check the number of outliers would be replaced
# PEStrad: (1 Flan, 6 Num, 7 Sci) 13 upper outliers, 1 Flan, 2 Num, 2Sci lower outliers 
# PESrobust: 0 Flan, 7 Num, 7 Sci upper outliers, 2 Flan,6 Num,7 Sci lower outliers 

# Trad: upper before lower, 28 in total, 
# 15 upper
# 13 lower, 8 cases more than the actual

# Robust: lower before upper, 31 in total
# 18 lower, 3 more than the actual
# 13 upper
 
# Get descriptive stats
# summarySE is a function of Rmism package
summarySE(Average, measurevar =  c("RTcorr"),
          groupvar = c("Task"), na.rm = TRUE)
```


```{r Checking distributions}

#### Distribution of RT
png("RTdistribution.png", width = 600, height = 600)
Average %>% ggplot(aes(RT, colour = Task)) +
  geom_histogram(binwidth = 0.3) +
  facet_wrap(~ Task) +
  labs(y = "RT", x = "Task",
        title = "Distribution of RT by Tasks") +
  theme_apa() +
  theme(legend.position = "none") 
dev.off

#### Distribution of RT used for PES 
png("RTtypedistribution.png", width = 600, height = 600)
Average %>% 
  gather("Type", "RT", 9:12) %>%
  ggplot(aes(RT, colour = Type)) +
  geom_histogram(binwidth = 0.3, alpha = 0.3) +
  facet_wrap(vars(Task)) +
  labs(y = "RT", x = "Task",
        title = "Distribution of RT type by Task") +
  theme_apa() +
  theme(legend.position = "bottom") 
dev.off
  

```


```{r Checking the corr rate}

# Checking whether there are NA in postC
filter(Average, is.na(postC))

# ID 94470 returns NA in postC
# Check corr rate
Average %>%
  filter(RandomID == 57502)

by(Average$IncorrRate, Average$Task, mean)

# ID 57502 & 94470 incorr rate too high in Flanker
# ID 57502 Incorr 118, 
# ID 94470 Incorr 116
# Remove them

Alltrial <- Alltrial %>%
  filter(RandomID != 57502 & RandomID != 94470)

Average <- Average %>%
  filter(RandomID != 57502 & RandomID != 94470)

write_csv(Alltrial, "ReadytoAnalyseData/Alltrial_564.csv")
write_csv(Average, "ReadytoAnalyseData/Average_564_OutlierRm.csv")

Average <- read_csv("ReadytoAnalyseData/Average_564_OutlierRm.csv")

# Determine the number of rows of Flanker NA, participants who do not make mistakes.

Average %>%
  group_by(Task) %>%
  summarise(sum = sum(is.na(PEStrad))) # Result is 110 in Flanker


```


```{r Check numbers of ppt}

Average %>%
  dplyr::group_by(Task) %>%
  dplyr::summarise(sum = sum(is.na(PEStrad)))

# Check missing value visually
vis_dat(df1[, 25:26])

write_csv(df, "ReadytoAnalyseData/Average_564_processed.csv")
write_csv(df1, "ReadytoAnalyseData/Average_564_NAreplaced.csv")

```

